\documentclass[10pt]{developercv}

\usepackage{enumitem}
\usepackage{multicol}
\usepackage{hyperref}
\usepackage{xcolor}

\begin{document}

\begin{multicols}{2}

\begin{minipage}[t]{0.45\textwidth}

\colorbox{black}{{\huge\textcolor{white}{\textbf{\MakeUppercase{John Doe}}}}}

\vspace{0.2cm}
{\large \textbf{Data Scientist}}

\vspace{0.2cm}
Data Scientist with 4+ years in Python, R, statistics, machine learning, and deep learning, supporting remote interviews and candidate evaluation. Experienced in regression, classification, clustering, and privacy-aware assessment for technical screening.
\end{minipage}
\vfill\null
\columnbreak

\begin{minipage}[t]{0.55\textwidth}

\hspace{1.5cm}\cvsect{PERSONAL DETAILS}

\hspace{0.5cm}\begin{tabular}{@{}ll}
\textbf{Address:} & \hspace{0.1cm} Austin, Texas, USA\\
\textbf{Phone:} & \hspace{0.1cm} +1 512 555 7812\\
\textbf{E-Mail:} & \hspace{0.1cm} \href{mailto:john.doe.analytics@gmail.com}{john.doe.analytics@gmail.com}\\
\textbf{LinkedIn:} & \hspace{0.1cm} \href{https://www.linkedin.com/in/johndoeanalytics}{linkedin.com/in/johndoeanalytics}\\
\end{tabular}

\end{minipage}

\end{multicols}

\cvsect{PROFESSIONAL EXPERIENCE}
\begin{entrylist}

  \entry
  {05/2024 -- Present\\\footnotesize{Austin, Texas, USA}}
  {Business Intelligence Analyst}
  {Horizon Technologies Inc.}
  {
  \begin{itemize}[leftmargin=*]
        \item Conducted remote AEM Developer interviews using Python and R scorecards, evaluating 18 candidates across statistics, probability, and ML fundamentals.
    \item Built SQL-backed interview rubrics and classification checks, improving calibration consistency across 12 interviewer sessions and reducing review rework by 8\%.
    \item Standardized confidentiality workflows in Python dashboards, securing candidate notes for 2K records and enabling flexible part-time screening coverage.
  \end{itemize}
  }


  \entry
  {08/2023 -- 04/2024\\\footnotesize{Dallas, Texas, USA}}
  {Graduate Data Analyst}
  {Northbridge Research Institute}
  {
  \begin{itemize}[leftmargin=*]
        \item Analyzed machine learning responses in R and Python, benchmarking 15K interview observations against statistics and probability criteria for candidate ranking.
    \item Applied regression and clustering models to assess technical depth, shortening evaluation turnaround by 6\% while preserving privacy controls.
  \end{itemize}
  }


  \entry
  {06/2021 -- 07/2023\\\footnotesize{Chicago, Illinois, USA}}
  {Data Analyst}
  {Sterling Consulting Group}
  {
  \begin{itemize}[leftmargin=*]
        \item Designed remote interview guides in SQL and Python for statistics, deep learning, and transformers, covering 22 client requisitions.
    \item Automated classification-based candidate summaries, reducing manual note synthesis by 12\% and improving interviewer handoff quality across 4K records.
    \item Validated CNN and RNN answers through structured assessments, increasing technical issue detection by 9\% during screening interviews.
  \end{itemize}
  }


  \entry
  {01/2021 -- 05/2021\\\footnotesize{Phoenix, Arizona, USA}}
  {Data Engineering Intern}
  {BluePeak Analytics}
  {
  \begin{itemize}[leftmargin=*]
        \item Built Python data pipelines and probability checks for internship interview datasets, improving analysis speed by 5\% over 2K records.
  \end{itemize}
  }

\end{entrylist}

\cvsect{EDUCATION}
\begin{entrylist}

  \entry
  {09/2022 -- Present}
  {Master of Science (Business Analytics)}
  {University of Texas at Dallas}
  {Graduate Merit Scholarship Recipient, GPA: 3.8/4.0 \\Focus: Business Analytics}


  \entry
  {08/2017 -- 05/2021}
  {Bachelor of Science (Computer Engineering)}
  {Arizona State University}
  {GPA: 3.7/4.0 \\Focus: Software engineering, databases, statistics}

\end{entrylist}

\vspace{0.5cm}
\cvsect{SKILLS}

\textbf{Technical Skills:} Python, R, Statistics, Probability, Machine Learning, Regression, Classification, Clustering, Deep Learning, Transformers

\textbf{Tech Stack:} Python, R, SQL, ML scoring, Remote interviews, Data privacy

\textbf{Soft Skills:} Confidentiality, Data privacy, Time flexibility, Remote collaboration, Structured communication


\cvsect{PROJECTS}
\begin{itemize}[leftmargin=*]
    \item \textbf{Remote Interview Scoring Model:} Created a Python and SQL scoring model for candidate interviews, improving rubric consistency by 7\% across 3K evaluations.
    \item \textbf{Privacy-Aware Screening Dashboard:} Built an R dashboard for confidential interview tracking, reducing manual reporting effort by 5\% for remote assessors.
\end{itemize}



\cvsect{CERTIFICATIONS}

Google Advanced Data Analytics Certificate, Microsoft Power BI Data Analyst Associate, AWS Certified Data Analytics Specialty




\cvsect{MISCELLANEOUS}

\textbf{Languages:} Fluent English, Conversational Spanish\\[0.05cm]

\textbf{Hobbies:} I love to host trivia nights. I also enjoy hiking, playing chess, and soccer.

\end{document}
