\documentclass[11pt, a4paper]{article}
\usepackage[a4paper, top=2.5cm, bottom=2.5cm, left=2cm, right=2cm]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{helvet}
\usepackage{hyperref}
\usepackage{xcolor}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\setlength{\parskip}{1em}

\begin{document}

\textbf{John Doe}\\
Austin, Texas, USA\\
+1 512 555 7812\\
\href{mailto:john.doe.analytics@gmail.com}{john.doe.analytics@gmail.com}\\
\href{https://www.linkedin.com/in/johndoeanalytics}{linkedin.com/in/johndoeanalytics}

\vspace{1cm}

\textbf{Hiring Team}\\
Risebird\\

\vspace{1cm}

\textbf{Data Scientist – John Doe}

Dear Hiring Team,

Risebird’s Data Scientist role aligns closely with my background in remote technical screening. At Horizon Technologies Inc., I conducted remote AEM Developer interviews using Python and R scorecards, evaluating 18 candidates across statistics, probability, and machine learning fundamentals. That work matches the role’s focus on part-time interviewing and analytical assessment, while keeping the process structured and consistent.

Across recent roles, I have supported the exact areas highlighted in the posting through hands-on evaluation work. At Northbridge Research Institute, I analyzed machine learning responses in R and Python, benchmarking 15K interview observations against statistics and probability criteria for candidate ranking. I also applied regression and clustering models to assess technical depth, which shortened evaluation turnaround by 6\% while preserving privacy controls. At Sterling Consulting Group, I designed remote interview guides for statistics, deep learning, and transformers, and validated CNN and RNN answers through structured assessments.

My work has also depended on clear coordination and careful handling of sensitive information. At Horizon Technologies Inc., I standardized confidentiality workflows in Python dashboards, securing candidate notes for 2K records and enabling flexible part-time screening coverage. That same process discipline supported smoother interviewer handoffs and reduced review rework across 12 interviewer sessions. It is the kind of operating style that fits remote interviewing well.

Risebird’s interview-as-a-service model and remote, on-demand support for hiring teams make this opportunity a strong match for my background. The chance to contribute to candidate screening with attention to confidentiality and data privacy is especially relevant. I would welcome the opportunity to support Risebird’s interviewing needs with consistent, flexible assessment work.

Sincerely,\\
John Doe

\end{document}